TINET+TECS: Component-based TCP/IP Protocol Stack for Embedded Systems

### 2017-01-05 ISORC2017/paper.tex
Update paper.tex

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{
\IEEEauthorblockN{Takuro Yamamoto}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
\and
\IEEEauthorblockN{Takuma Hara}
\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
\and
\IEEEauthorblockN{Takuya Ishikawa}
\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
\and
\IEEEauthorblockN{Hiroshi Oyama}
\IEEEauthorblockA{OKUMA Corporation}
\and
\IEEEauthorblockN{Hiroaki Takada}
\IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
\and
\IEEEauthorblockN{Takuya Azumi}
\IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
}

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
% \author{
% \IEEEauthorblockN{
% Takuro Yamamoto\IEEEauthorrefmark{1},
% Takuma Hara\IEEEauthorrefmark{2},
% Takuya Ishikawa\IEEEauthorrefmark{2}, 
% Hiroshi Oyama\IEEEauthorrefmark{3},
% Hiroaki Takada\IEEEauthorrefmark{2} and
% Takuya Azumi\IEEEauthorrefmark{1}}
% \IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
% \IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
% \IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
% }

@@

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
This paper evaluates the overheads of execution time and memory consumption and amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.

@@

@@

\subsection{send/receive specifier}

@@

@@

\begin{table}[t]
    \centering
    \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:Evaluation_Board_Environment}
\end{table}

@@

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
% \author{
% \IEEEauthorblockN{Takuro Yamamoto}
% \IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
% \and
% \IEEEauthorblockN{Takuma Hara}
% \IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
% \and
% \IEEEauthorblockN{Takuya Ishikawa}
% \IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
% \and
% \IEEEauthorblockN{Hiroshi Oyama}
% \IEEEauthorblockA{OKUMA Corporation}
% \and
% \IEEEauthorblockN{Hiroaki Takada}
% \IEEEauthorblockA{Graduate School of Information Science\\Nagoya University}
% \and
% \IEEEauthorblockN{Takuya Azumi}
% \IEEEauthorblockA{Graduate School of Engineering Science\\Osaka University}
% }

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
\author{
\IEEEauthorblockN{
Takuro Yamamoto\IEEEauthorrefmark{1},
Takuma Hara\IEEEauthorrefmark{2},
Takuya Ishikawa\IEEEauthorrefmark{2}, 
Hiroshi Oyama\IEEEauthorrefmark{3},
Hiroaki Takada\IEEEauthorrefmark{2} and
Takuya Azumi\IEEEauthorrefmark{1}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Graduate School of Engineering Science, Osaka University}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Graduate School of Information Science, Nagoya University}
\IEEEauthorblockA{\IEEEauthorrefmark{3}OKUMA Corporation}
}

@@

In this paper, component-based TCP/IP protocol stack, i.e., componentized TINET, is proposed to improve the configurability and scalability of software.
TECS (TOPPERS Embedded Component System) \cite{par:TECS} is utilized to componentize TINET, because TECS is a component system suitable for embedded systems.
TECS supports static configuration, which statically defines component behaviors and interconnections, thus TECS can optimize the overhead of componentization.
This paper evaluates the overheads of execution time and memory consumption and the amount of code line change for adding/removing the functionalities, which demonstrates TINET+TECS can improve the configurability with small overheads.

@@

The components of protocol stack for TINET+TECS is shown as Fig. \ref{fig:ComponentProtocolStack}.
Note that some small particle components such as a kernel object, dataqueques, and semaphores are omitted to simplify the component diagram.
In TINET+TECS, the components are divided for each protocol, and the functionalities such as input function and output function are defined as each a component.
Therefore, software visibility is improving because of small grain components.

To utilize the protocol stack as same as the original TINET, communication object components such as tTCPCEP, tUDPCEP, and tREP are defined as an interface between TINET+TECS and an application.
The communication object component is a component corresponding to a CEP or REP of the original TINET.
An application developers can utilize the TINET+TECS functionalities by generating and combining as many components as necessary.

The protocol stack of TINET+TECS supports coexistence of multiple protocols.
By developing the IPv6 and Point-to-Point Protocol (PPP) components, TINET+TECS can make IPv4 and IPv6 coexist and support PPP without a modification of component implementation.

@@

\subsection{Memory allocator component}

\subsubsection{send/receive specifier}

@@

\subsection{Network timer component}

@@

\subsection{Evaluation environment}

GR-PEACH is employed as the evaluation board.
We connected the board and the host PC with a LAN cable, and evaluated the data transmission and reception.
The detail specification of the board is shown in TABLE \ref{tab:EvaluationBoardEnvironment}.
We also employ TINET 1.5.4 and the compiler arm-none-eabi--gcc 5.2.

\begin{table}[t]
    \centering
    \caption{Evaluation Board Environment}
    \begin{tabular}{l|l}
        \hline\hline
        Board           &   GR-PEACH                \\
        CPU             &   Cortex-A9 RZ/A1H 400MHz \\
        Flash ROM       &   8 MB                    \\
        RAM             &   10 MB                   \\
        LAN Controller  &   LAN8710A                \\
        \hline
    \end{tabular}
    \label{tab:EvaluationBoardEnvironment}
\end{table}

@@

The authers would like to thank OO for supporting this research.
This work is supported by JSPS KAKENHI Grant Number 15H05305.
